\begin{enumerate}
    \item All executive and non-executive positions will be elected positions.
    \item Executive positions may only be held by youth full members who have been registered with the Company/Crew for at least one year.\footnote{An exception can be made based on the current group registration.}
    \item There should be at least one member from the Venturer section, one from the Rover section. \footnotemark[\value{footnote}]
    \item Executive positions within the Company/Crew are President, Vice President, Treasurer, Secretary, Quartermaster, and Contact Adviser.
    \item Non-executive positions within the Company/Crew is Master at Arms and Adviser.
    \item Executive and Non-Executive position terms begin and end with the scouting year.
    \item Annual elections for executive positions are to be held during the month, 3 months prior to the end of the scouting year.
    \item The executive council, with the approval of the contact Adviser, has the authority to suspend any member of the Company/Crew for any duration or permanently revoked membership, as a disciplinary action.
    \item The executive council, with thek approval of the contact Adviser, has the authority to restrict privileges, as a disciplinary action.
\end{enumerate}

\subsection{Duties of the President}
\begin{enumerate}
    \item Organize executive council and Company/Crew meetings and ensure all members are notified.
    \item Provide leadership to the Company/Crew at meetings and activities.
    \item Chair executive council and Company/Crew meetings.
    \item Ensure that all members and Advisers are kept informed.
    \item Attend monthly Group Committee meetings, representing the Company/Crew, including making presentations and other related tasks.
\end{enumerate}

\subsection{Duties of the Vice-President}
\begin{enumerate}
    \item Act in place of the President when required.
    \item Provide leadership to the Company/Crew at meetings and events.
    \item Keep absentee members informed of current and upcoming activities.
    \item Execute such tasks as assigned by the President.
\end{enumerate}

\subsection{Duties of the Secretary}
\begin{enumerate}
    \item Maintain a record of attendance and notices of absence for all meetings.
    \item Record proper minutes of executive council and Company/Crew meetings.
    Provide minutes to all members of the meeting.
    \item Report on all internal communication by the Company/Crew.
    \item Keep an up-to-date membership list with phone numbers and e-mail addresses.
    \item Keep copies of the minutes from Group Committee meetings.
    \item Keep copies of the Company/Crew Constitution and Code of Conduct.
\end{enumerate}

\subsection{Duties of the Treasurer}
\begin{enumerate}
    \item Maintain up-to-date records of the Company/Crew financial state, supported by documented accounts or revenues and expenses.
    \item Submit Company/Crew financial records for Advisers and executive council for review quarterly.
    \item Submit Company/Crew financial records to the Group Committee for auditing annually in September.
\end{enumerate}

\subsection{Duties of the Quartermaster}
\begin{enumerate}
    \item Maintain a record of all equipment belonging to the Company/Crew.
    \item Ensure the storage and maintenance of equipment belonging to the Company/Crew.
    \item Provide a list of equipment to members planning events for sign-out and use at said events.
    \item Ensure all equipment is necessary and in good repair.
\end{enumerate}

\subsection{Duties of the Master at Arms}
\begin{enumerate}
    \item Ensure adherence to Robert's Rules of Order.
    \item Ensure adherence to the Constitution and Code of Conduct.
\end{enumerate}

\subsection{Duties of the Advisers}
\begin{enumerate}
    \item To assist the Company/Crew and its members to achieve their objectives, whether group or individual.
    \item Advisers suggest and advise, but do not order members, excepting that Advisers have veto powers on issues of safety, or any laws/by-laws that come into play.
    \item Activities may be held without Advisers present after notification (with complete details) has been provided to the Advisers, and the Advisers have approved the activities.
    \item The contact Adviser is ultimately responsible to the Group Committee for the actions of the Company/Crew.
\end{enumerate}
A motion of abandonment of position may be raised after any executive has missed three consecutive meetings without a valid reason or has failed to carry out their duties without a valid reason.
If for any reason, the members of the Company/Crew wish to add or remove an Adviser, all changes in the Adviser team must first be approved by the Group Commissioner.