Any stipulation made to a member of the Company/Crew for compliance will also apply to all members of the Company/Crew.
All Service Corps members will be placed in one of three categories.
\subsection{Primary}
Those youth and adult members who are registered with the Company/Crew as their primary group.
These members shall complete an official Scouts Canada application for membership and submit to the Group Registrar annually.
These members are an active part of the Company/Crew and contribute to the organization or execution of events as well as attend regular meetings.
The minimum annual requirements of the primary members are as follows: two major events, five elective events, three fundraiser events, all required training, and 75\% of meetings.
\subsection{Secondary}
Those youth and adult members who are registered with another Scouts Canada group and are registered as a duplicate with the Company/Crew.
These members shall complete an official Scouts Canada application for membership, print "DUPLICATE" on the top of the form along with their home group and membership number (if possible) and submit to the Group Registrar annually.
These members are an active part of the Company/Crew and contribute to the organization or execution of events as well as attend regular meetings.
The minimum annual requirements of the secondary members are as follows: two major events, two elective events, two fundraiser events, required training, and 50\% of meetings.
\subsection{Honorary}
Those youth and adult members who are not necessarily registered with Scouts Canada.
These members are not necessarily active members of the Company/Crew and contribute to the organization or execution of events as well as attend regular meetings.
These members must be voted into the group.
\subsection{Applicants}
\begin{enumerate}
	\item Membership of the Company/Crew shall be open to anyone meeting the age criteria established by the BP\&P of Scouts Canada and are willing to live up to the Company/Crew promise, the Aims and Principals of Scouts Canada, and accept the Constitution of the Company/Crew. 
	\item Applicants for full membership shall undergo a trial period, consisting of two business meetings and one major service-oriented activity or two minor service-oriented activity.
	\item Applicants for membership after shall undergo an interview with at least two members of the executive council.
	Interviewers can approve, or disapprove\footnote{To deny recruitment, the executive council Council must provide reason(s) and need the approval of the Advisers and Group Commissioner.} their application to join.
	\item Applicants for full membership shall make the Scout Promise to the assembled Company/Crew upon investiture. 
\end{enumerate}
\subsection{Responsibilities}
\begin{enumerate}
	\item Members of the Company/Crew must abide by the Company/Crew Constitution and Code of Conduct.
	Failure to abide by the Constitution and Code of Conduct will be reviewed by the executive council and can result in disciplinary action.
	\item Members of the Company/Crew must provide a valid reason for missing meetings.
	Failure to do so three times consecutively automatically result in the suspension of voting privileges.\footnote{An exception can be made for members who are registered within Service Corp but are at school.}
	\item Members of the Company/Crew must provide notice to the executive council at least two weeks in advance of renouncing their membership.
\end{enumerate}
\subsection{Rights \& Privileges}
\begin{enumerate}
	\item Members of the Company/Crew have the privilege to vote at Company/Crew activities.
	\item Members of the Company/Crew have the privilege to earn financial compensation as detailed by Service Corps Financial Compensation.
	\item Members of the Company/Crew have the right to wear and buy Company/Crew Branded equipment.
\end{enumerate}