\begin{enumerate}
	\item Membership of the Company/Crew/Unit shall be open to anyone meeting the age criteria established by the "Bylaw, Policies and Procedures" of Scouts Canada and are willing to live up to the Company/Crew/Unit promise, the Aims and Principals of Scouts Canada and Girl Guides of Canada and accept the Constitution of the Company/Crew/Unit. 
	\item Applicants shall undergo a trial period, consisting of two business meetings and one major service-oriented activity or two minor service-oriented activity, after which time at least two members of the Executive will interview, approve, or disapprove\footnote{To deny recruitment the Executive Council must provide reason(s) and need the approval of the Advisors and Group Commissioner. The Executive Council must work with the recruit to find a more suitable Company/Crew/Unit.} their application to join.
	\item Applicants shall make the Scout/Guide Promise to the assembled Company/Crew/Unit upon investiture. 
	\item Members of the Company/Crew/Unit must abide by the Company/Crew/Unit Code of Conduct. Failure to abide by the Code of Conduct will be reviewed by the Executive and can result in disciplinary action. 
	\item Members of the Company/Crew/Unit must abide by Robert's Rules of Order for all Company/Crew/Unit meetings in all cases which it does not conflict with the Company/Crew/Unit Constitution or Code of Conduct.
	\item Members of the Company/Crew/Unit must report any violation of the Company/Crew/Unit Constitution or Code of Conduct to the Executive in a formal and accountable way.
	\item Members of the Company/Crew/Unit must provide notice to the Executive in a formal and accountable way if they are unable to attend a meeting before the meeting takes place.
	\item Members of the Company/Crew/Unit will be subject to a suspension of voting privileges if they miss three meetings without valid reason. Failure to abide will result in review by the Executive and can result in disciplinary action. An exception to this rule applies to youth members who are registered within Service Corp but are away at school.
	\item The Executive, with the approval of the contact Advisor, has the authority to suspend any member of the Company/Crew/Unit for short durations for violations of the Service Corps Code of Conduct. 
	\item Membership in the Company/Crew/Unit can be reviewed and possibly permanently revoked by Service Corps if any member does not comply with this Constitution, the Code of Conduct, Scouts Canada's "Bylaws, Policies and Procedures", Canadian Law, fails to live up to their Scout/Guide Promise, or any combination thereof.
	\item Any member may resign from the Company/Crew/Unit by providing notice of his/her intentions to the Executive at least two weeks in advance.
\end{enumerate}
Any stipulation made to a member of the Company/Crew/Unit for compliance will also apply to all members of the Company/Crew/Unit. 
Scouting/Guiding members who participate in the Company/Crew/Unit activities will be placed in one of three categories. Those youth and adults in the Primary and Secondary categories shall be considered FULL members of the Company/Crew/Unit for all purposes including voting privileges. 
\subsection{Primary}
Those youth and adult members who are registered with the Company/Crew/Unit as their primary group. Youth members are typically of Venturer and Rover age. These members shall complete an official Scouts Canada application for membership and submit to the Group Registrar annually. These youth and adults are active members of the Company/Crew/Unit and contribute to the organization or execution of events as well as attend regular meetings. The minimum annual requirements of the primary members are as follows: two major events (in addition to any required training), five elective events, three fundraiser events, and 75\% of meetings.
\subsection{Secondary}
Those youth and adult members who are registered with another Scouts Canada group and are registered as a duplicate with the Company/Crew/Unit or are registered members of Girl Guides of Canada. These members shall complete an official Scouts Canada application for membership, print "DUPLICATE" on the top of the form along with their home group and membership number (if possible) and submit to the Group Registrar annually.\footnote{Rangers are not required to fill out a Scouts Canada registration form.} These youth and adults are active members of the Company/Crew/Unit and contribute to the organization or execution of events as well as attend regular meetings. The minimum annual requirements of the secondary members are as follows: two major events (in addition to any required training), two elective events, two fundraiser events, and 50\% of meetings. 
\subsection{Auxiliary}
Those youth and adult members who are registered with another Group within Scouts Canada or Girl Guides of Canada and who participate in the Company/Crew/Unit activities to complete their required community service, or as a group activity. If training is being offered for a specific event attendance is mandatory.