\begin{enumerate}
    \item Membership of the Company/Crew/Unit shall be open to anyone meeting the age criteria established by the BP\&P and are willing to live up to the Company/Crew/Unit promise, the Aims and Principals of Scouts Canada and Girl Guides of Canada, and accept the Constitution of the Company/Crew/Unit.
    \item Applicants shall undergo a trial period, consisting of two business meetings and one major service-oriented activity or two minor service-oriented activity, after which time at least two members of the Executive will interview, approve, or disapprove\footnote{To deny recruitment the Executive Council must provide reason(s) and need the approval of the Advisors and Group Commissioner. The Executive Council must work with the recruit to find a more suitable Company/Crew/Unit.} their application to join.
    \item Applicants shall make the Scout/Guide Promise to the assembled Company/Crew/Unit upon investiture.
    \item Advisors are considered members Company/Crew/Unit but are not subject to the age restrictions or the application process.
    \item Members of the Company/Crew/Unit must abide by the Company/Crew/Unit Code of Conduct.
    \item Members of the Company/Crew/Unit must attend any mandatory training for an event the member attends.
    \item Members of the Company/Crew/Unit must abide by Robert's Rules of Order for all Company/Crew/Unit meetings in all cases which it does not conflict with the Company/Crew/Unit Constitution or Code of Conduct.
    \item Members of the Company/Crew/Unit must report any violation of the Company/Crew/Unit Constitution or Code of Conduct to the Executive in a formal and accountable way.
    \item Members of the Company/Crew/Unit must provide notice to the Executive in a formal and accountable way if they are unable to attend a meeting before the meeting takes place.
    \item Members of the Company/Crew/Unit will be subject to a suspension of voting privileges if they miss three meetings without valid reason.\footnote{An exception to this rule may be made to youth members who are registered within Service Corp but are away at school.}
    \item The Executive, with the approval of the contact Advisor, has the authority to perform of the following actions to any member if that member does not comply with this Constitution, the Code of Conduct, BP\&P, Canadian Law, fails to live up to their Scout/Guide Promise, or any combination thereof.
    \begin{enumerate}
        \item Suspension of the member's voting privileges.
        \item Suspend the member of the Company/Crew/Unit for short durations.
        \item Permanently revoked the membership of the member.
        \item Any other disciplinary action deemed appropriate by the Executive, and the contact Advisor.
    \end{enumerate}
    \item Any member may resign from the Company/Crew/Unit by providing notice of his/her intentions to the Executive at least two weeks in advance.
\end{enumerate}
Any stipulation made to a member of the Company/Crew/Unit for compliance will also apply to all members of the Company/Crew/Unit.
Scouting/Guiding members who participate in the Company/Crew/Unit activities will be placed in one of three categories.
Those youths and adults in the Primary and Secondary categories shall be considered FULL members of the Company/Crew/Unit for all purposes, including voting privileges.
Those youths and adults in the Auxiliary category shall not have voting privileges.

\subsection{Primary}\label{subsec:primary}
Those youth and adult members who are registered with the Company/Crew/Unit as their primary group.
The minimum annual requirements of the primary members are as follows: two major events (in addition to any required training), five elective events, three fundraiser events, and 75\% of meetings.

\subsection{Secondary}\label{subsec:secondary}
Those youth and adult members who are registered with another Scouts Canada or Girl Guides of Canada group and are registered as a duplicate with the Company/Crew/Unit.
The minimum annual requirements of the secondary members are as follows: two major events (in addition to any required training), two elective events, two fundraiser events, and 50\% of meetings.

\subsection{Auxiliary}\label{subsec:auxiliary}
Those youth and adult members who are registered with another Group within Scouts Canada or Girl Guides of Canada who participate in the Company/Crew/Unit activities.