\documentclass{Service_Corps_Document}
\stdSetup
\begin{document}
    \def \Title {Code of Conduct}
    \def \Company {Service Corps}
    \def \versionNumber {3.0}
    \stdFooter
    \begin{titlepage}
        \stdTitlePage
    \end{titlepage}
    \begin{enumerate}
        \item Follow the Scouts Canada Promise, the Law, Motto, and BP\&P (BY-LAW, POLICIES, AND PROCEDURES) or the Girl Guides of Canada Vision, Mission, Values, Promise, Law, and Code of Conduct.
        \item Follow the Service Corps Constitution.
        \item No verbal or physical abuse.
        \item No mean spirited, unkind or offensive remarks \textendash be respectful and considerate of other people's feelings.
        \item No use of cellular phones for personal purposes during the meetings.
        \item If members within the Company/ Crew/Unit are dating, there should be no flirting or romantic behaviors displayed during Scouting/Guiding meetings or events.
        \item Work cooperatively as a team member with the Executive Council as well as the rest of the members of the Company/Crew/Unit.
        \item All communications regarding any Scouting/Guiding activity sent via email or Social Media must be copied to at least 2 Scouters/Guiders to make sure the information is kept as group knowledge and for record keeping.
        Texting should not be used as a primary tool to relay Scouting/Guiding activity communications.
        \item For all events where members are communicating using a radio, the member will follow RIC-22.
        \item Any infractions to the Code of Conduct may be raised with the Executive Council, which will decide the appropriate course of action to follow.

    \end{enumerate}
\end{document}